The title

### 2023-03-21 doc/multiverse.Rmd
Line removal
Update headers in results chunk

<!------------------------------------>
<!-- Auto-generated chunks go here: -->
<!------------------------------------>

\clearpage

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by BMI
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).

@@

We estimated the effect of sleep regularity on physical activity by BMI.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by SES
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).

@@

We estimated the effect of sleep regularity on physical activity by SES.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by sex
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).

@@

We estimated the effect of sleep regularity on physical activity by sex.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by weekday
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).

@@

We estimated the effect of sleep regularity on physical activity by weekday.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by season
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).

@@

We estimated the effect of sleep regularity on physical activity by season.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by region
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).

@@

We estimated the effect of sleep regularity on physical activity by region.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).

@@

### The effects of physical activity volume on sleep

@@

We estimated the effect of sleep duration on physical activity by daylight hours
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).

@@

We estimated the effect of sleep regularity on physical activity by daylight hours.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).

@@

### The effects of physical activity volume on sleep

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear_location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)

```{r sleep-outcomes-by-wear_location}
papaja::apa_table(
  model_tables_wear_location$sleep$data,
  caption = model_tables_wear_location$sleep$caption,
  note = model_tables_wear_location$sleep$note,
  col_spanners = model_tables_wear_location$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

We estimated how physical activity intensity affects sleep across wear location
We present the results in Table \@ref(tab:sleep-outcomes-by-wear_location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).

@@

We estimated the effect of sleep duration on physical activity by wear location
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).

```{r pa-outcomes-by-wear_location}
papaja::apa_table(
  model_tables_wear_location$physical_activity$data,
  caption = model_tables_wear_location$physical_activity$caption,
  note = model_tables_wear_location$physical_activity$note,
  col_spanners = model_tables_wear_location$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

We estimated the effect of sleep efficiency on physical activity by wear location.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear_location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).

@@

We estimated the effect of sleep regularity on physical activity by wear location.
Results are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).

>>>>

<!------------------------------------>
<!-- Auto-generated chunks go here: -->
<!------------------------------------>
\clearpage

@@

### The effects of physical activity volume on sleep by BMI

@@

We estimated the effect of sleep duration on physical activity by BMI
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-bmi).

@@

We estimated the effect of sleep regularity on physical activity by BMI.
Results are presented in Table \@ref(tab:pa-outcomes-by-bmi) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-bmi).

@@

### The effects of physical activity volume on sleep by SES

@@

We estimated the effect of sleep duration on physical activity by SES
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-ses).

@@

We estimated the effect of sleep regularity on physical activity by SES.
Results are presented in Table \@ref(tab:pa-outcomes-by-ses) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-ses).

@@

### The effects of physical activity volume on sleep by sex

@@

We estimated the effect of sleep duration on physical activity by sex
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-sex).

@@

We estimated the effect of sleep regularity on physical activity by sex.
Results are presented in Table \@ref(tab:pa-outcomes-by-sex) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-sex).

@@

### The effects of physical activity volume on sleep by weekday

@@

We estimated the effect of sleep duration on physical activity by weekday
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-weekday).

@@

We estimated the effect of sleep regularity on physical activity by weekday.
Results are presented in Table \@ref(tab:pa-outcomes-by-weekday) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-weekday).

@@

### The effects of physical activity volume on sleep by season

@@

We estimated the effect of sleep duration on physical activity by season
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-season).

@@

We estimated the effect of sleep regularity on physical activity by season.
Results are presented in Table \@ref(tab:pa-outcomes-by-season) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-season).

@@

### The effects of physical activity volume on sleep by region

@@

We estimated the effect of sleep duration on physical activity by region
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-region).

@@

We estimated the effect of sleep regularity on physical activity by region.
Results are presented in Table \@ref(tab:pa-outcomes-by-region) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-region).

@@

### The effects of physical activity volume on sleep by daylight hours

@@

We estimated the effect of sleep duration on physical activity by daylight hours
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-daylight).

@@

We estimated the effect of sleep regularity on physical activity by daylight hours.
Results are presented in Table \@ref(tab:pa-outcomes-by-daylight) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-daylight).

@@

### The effects of physical activity volume on sleep by wear location

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by wear location, and the results are presented in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-volume-fig-by-wear-location)

```{r sleep-outcomes-by-wear-location}
papaja::apa_table(
  model_tables_wear_location$sleep$data,
  caption = model_tables_wear_location$sleep$caption,
  note = model_tables_wear_location$sleep$note,
  col_spanners = model_tables_wear_location$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

We estimated how physical activity intensity affects sleep across wear location
We present the results in Table \@ref(tab:sleep-outcomes-by-wear-location) and Figure \@ref(fig:sleep-by-intensity-fig-by-wear-location).

@@

We estimated the effect of sleep duration on physical activity by wear location
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-duration-fig-by-wear-location).

```{r pa-outcomes-by-wear-location}
papaja::apa_table(
  model_tables_wear_location$physical_activity$data,
  caption = model_tables_wear_location$physical_activity$caption,
  note = model_tables_wear_location$physical_activity$note,
  col_spanners = model_tables_wear_location$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

@@

We estimated the effect of sleep efficiency on physical activity by wear location.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-by-wear-location).

@@

We estimated the effect of sleep regularity on physical activity by wear location.
Results are presented in Table \@ref(tab:pa-outcomes-by-wear-location) and Figure \@ref(fig:PA-by-sleep-regularity-fig-by-wear-location).
